Enhancement of SDR in Thessaloniki

### 2024-04-19 GHI_enh_03_process.tex
Commit 2024-04-19 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-08}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-19}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-19 10:26:46.8 athan@sagan GHI_enh_03_process.R 3.634787 mins
\end{verbatim}

### 2024-04-19 GHI_enh_04_investigate.tex
Commit 2024-04-19 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-14}

@@

lmD: 1.566006 +/- 0.108321

lmY: 1.566022 +/- 0.108322

Arima: 1.566405 +/- 0.146687

@@

lmD: 0.950804 +/- 0.155249

lmY: 0.950827 +/- 0.155251

Arima: 1.022268 +/- 0.236917

@@

lmD: 1.086985 +/- 0.167871

lmY: 1.087013 +/- 0.167874

Arima: 1.159971 +/- 0.251086

@@

lmD: 1.034078 +/- 0.239285

lmY: 1.034088 +/- 0.23929

Arima: 1.03413 +/- 0.363491

@@

lmD: 0.944568 +/- 0.252832

lmY: 0.944578 +/- 0.252837

Arima: 0.944623 +/- 0.387039

@@

lmD: 1.109672 +/- 0.07725

lmY: 1.109686 +/- 0.077252

Arima: 1.109689 +/- 0.115906

@@

lmD: 1.167512 +/- 0.073583

lmY: 1.167525 +/- 0.073584

Arima: 1.167532 +/- 0.106265

@@

lmD: 33.66024 +/- 5.69273

lmY: 33.6608 +/- 5.692829

Arima: 33.721354 +/- 8.881459

@@

lmD: 0.003266 +/- 0.000271

lmY: 0.003266 +/- 0.000271

Arima: 0.003291 +/- 0.000364

@@

lmD: 0.001715 +/- 0.000278

lmY: 0.001715 +/- 0.000278

Arima: 0.001886 +/- 0.000465

@@

lmD: 0.001677 +/- 0.000314

lmY: 0.001677 +/- 0.000314

Arima: 0.001849 +/- 0.000512

@@

lmD: 0.00184 +/- 0.000301

lmY: 0.00184 +/- 0.000301

Arima: 0.00184 +/- 0.000473

@@

lmD: 0.001768 +/- 0.000292

lmY: 0.001768 +/- 0.000292

Arima: 0.001768 +/- 0.000451

@@

lmD: 0.002432 +/- 0.000235

lmY: 0.002432 +/- 0.000235

Arima: 0.002432 +/- 0.000369

@@

lmD: 0.002624 +/- 0.000229

lmY: 0.002624 +/- 0.000229

Arima: 0.002624 +/- 0.000346

@@

lmD: 0.977006 +/- 0.143935

lmY: 0.977029 +/- 0.143937

Arima: 1.040956 +/- 0.218636

@@

lmD: 0.817503 +/- 0.103432

lmY: 0.817514 +/- 0.103434

Arima: 0.817505 +/- 0.120041

@@

lmD: 0.216071 +/- 0.038072

lmY: 0.216075 +/- 0.038073

Arima: 0.216075 +/- 0.041418

@@

lmD: 0.190931 +/- 0.037875

lmY: 0.190936 +/- 0.037876

Arima: 0.190936 +/- 0.040087

@@

lmD: 0.485676 +/- 0.046388

lmY: 0.485682 +/- 0.046389

Arima: 0.485682 +/- 0.055179

@@

lmD: -0.00734 +/- 0.019077

lmY: -0.007339 +/- 0.019077

Arima: -0.007339 +/- 0.019267

@@

lmD: -0.027816 +/- 0.017696

lmY: -0.027816 +/- 0.017696

Arima: -0.027816 +/- 0.017858

@@

lmD: 0.49203 +/- 0.073274

lmY: 0.492037 +/- 0.073275

Arima: 0.492032 +/- 0.081403

@@

lmD: 0.595557 +/- 0.083417

lmY: 0.595566 +/- 0.083419

Arima: 0.59556 +/- 0.094857

@@

lmD: 1.467857 +/- 0.152656

lmY: 1.46788 +/- 0.152659

Arima: 1.467877 +/- 0.18431

@@

lmD: 0.001336 +/- 0.000137

lmY: 0.001336 +/- 0.000137

Arima: 0.001336 +/- 0.000157

@@

lmD: 0.000423 +/- 5.9e-05

lmY: 0.000423 +/- 5.9e-05

Arima: 0.000423 +/- 6.7e-05

@@

lmD: 0.000372 +/- 6.1e-05

lmY: 0.000372 +/- 6.1e-05

Arima: 0.000372 +/- 6.8e-05

@@

lmD: 2.1e-05 +/- 3.2e-05

lmY: 2.1e-05 +/- 3.2e-05

Arima: 2.1e-05 +/- 3.6e-05

@@

lmD: -1.2e-05 +/- 2.9e-05

lmY: -1.2e-05 +/- 2.9e-05

Arima: -1.2e-05 +/- 3.4e-05

@@

lmD: 0.000922 +/- 0.000106

lmY: 0.000922 +/- 0.000106

Arima: 0.000922 +/- 0.00012

@@

lmD: 0.001074 +/- 0.000117

lmY: 0.001074 +/- 0.000117

Arima: 0.001074 +/- 0.000134

@@

lmD: 0.036561 +/- 0.003622

lmY: 0.036562 +/- 0.003622

Arima: 0.036562 +/- 0.004204

@@

lmD: 0.187208 +/- 0.249476

lmY: 0.187246 +/- 0.24948

Arima: 0.171775 +/- 0.364628

@@

lmD: 0.049774 +/- 0.192505

lmY: 0.049798 +/- 0.192508

Arima: 0.008548 +/- 0.346363

@@

lmD: 0.091248 +/- 0.191453

lmY: 0.091272 +/- 0.191456

Arima: 0.049975 +/- 0.33542

@@

lmD: -0.069532 +/- 0.179279

lmY: -0.06952 +/- 0.179282

Arima: -0.124647 +/- 0.339466

@@

lmD: -0.089703 +/- 0.178956

lmY: -0.089692 +/- 0.178959

Arima: -0.144328 +/- 0.338161

@@

lmD: 0.16704 +/- 0.22968

lmY: 0.167077 +/- 0.229683

Arima: 0.146398 +/- 0.353614

@@

lmD: 0.17703 +/- 0.238162

lmY: 0.177067 +/- 0.238165

Arima: 0.158966 +/- 0.358093

@@

lmD: 0.368357 +/- 0.253498

lmY: 0.368383 +/- 0.253502

Arima: 0.36844 +/- 0.258271

@@

lmD: 0.000508 +/- 0.000281

lmY: 0.000509 +/- 0.000281

Arima: 0.000508 +/- 0.000318

@@

lmD: 0.000356 +/- 0.000214

lmY: 0.000356 +/- 0.000214

Arima: 0.000349 +/- 0.000265

@@

lmD: 0.000399 +/- 0.000221

lmY: 0.000399 +/- 0.000221

Arima: 0.000392 +/- 0.00027

@@

lmD: 0.000168 +/- 0.000199

lmY: 0.000168 +/- 0.000199

Arima: 0.000157 +/- 0.000257

@@

lmD: 0.000155 +/- 0.000199

lmY: 0.000155 +/- 0.000199

Arima: 0.000144 +/- 0.000256

@@

lmD: 0.000509 +/- 0.000261

lmY: 0.000509 +/- 0.000261

Arima: 0.000508 +/- 3e-04

@@

lmD: 0.00051 +/- 0.00027

lmY: 0.00051 +/- 0.00027

Arima: 0.000509 +/- 0.000307

@@

lmD: 0.008776 +/- 0.005507

lmY: 0.008777 +/- 0.005507

Arima: 0.008799 +/- 0.005722

@@

Arima: 0.216075 +/- 0.041418

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

lmY: 341.6364 +/- 36.57038

@@

lmY: 122.2229 +/- 11.42113

@@

lmY: 0.232986 +/- 0.055703

@@

lmY: 0.183685 +/- 0.040872

@@

\begin{verbatim}
2024-04-14 00:48:00.3 athan@tyler GHI_enh_04_investigate.R 1.346105 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-19}

@@

lmD: 1.552161 +/- 0.104876

lmY: 1.552176 +/- 0.104878

Arima: 1.552549 +/- 0.14034

@@

lmD: 0.954836 +/- 0.154734

lmY: 0.954859 +/- 0.154736

Arima: 1.024507 +/- 0.23503

@@

lmD: 1.088987 +/- 0.16743

lmY: 1.089013 +/- 0.167433

Arima: 1.160151 +/- 0.24838

@@

lmD: 1.050842 +/- 0.240164

lmY: 1.050851 +/- 0.240168

Arima: 1.050895 +/- 0.364666

@@

lmD: 0.958299 +/- 0.253655

lmY: 0.958309 +/- 0.25366

Arima: 0.958355 +/- 0.388216

@@

lmD: 1.089066 +/- 0.07424

lmY: 1.089079 +/- 0.074241

Arima: 1.089082 +/- 0.109498

@@

lmD: 1.136243 +/- 0.070602

lmY: 1.136256 +/- 0.070603

Arima: 1.136263 +/- 0.100583

@@

lmD: 33.75698 +/- 5.702807

lmY: 33.75752 +/- 5.702906

Arima: 33.816428 +/- 8.918367

@@

lmD: 0.003302 +/- 0.00027

lmY: 0.003302 +/- 0.00027

Arima: 0.003326 +/- 0.000357

@@

lmD: 0.001743 +/- 0.000278

lmY: 0.001743 +/- 0.000278

Arima: 0.001906 +/- 0.000459

@@

lmD: 0.001718 +/- 0.000312

lmY: 0.001718 +/- 0.000312

Arima: 0.001883 +/- 0.000503

@@

lmD: 0.001896 +/- 0.000307

lmY: 0.001896 +/- 0.000307

Arima: 0.001896 +/- 0.000479

@@

lmD: 0.001823 +/- 0.000299

lmY: 0.001823 +/- 0.000299

Arima: 0.001823 +/- 0.00046

@@

lmD: 0.002414 +/- 0.000233

lmY: 0.002414 +/- 0.000233

Arima: 0.002414 +/- 0.000362

@@

lmD: 0.002624 +/- 0.000228

lmY: 0.002624 +/- 0.000228

Arima: 0.002624 +/- 0.000339

@@

lmD: 0.988112 +/- 0.144355

lmY: 0.988134 +/- 0.144358

Arima: 1.051184 +/- 0.218585

@@

lmD: 0.816129 +/- 0.101923

lmY: 0.816139 +/- 0.101925

Arima: 0.816132 +/- 0.119665

@@

lmD: 0.215792 +/- 0.037414

lmY: 0.215795 +/- 0.037415

Arima: 0.215796 +/- 0.040986

@@

lmD: 0.181869 +/- 0.03711

lmY: 0.181874 +/- 0.037111

Arima: 0.181874 +/- 0.039209

@@

lmD: 0.481659 +/- 0.045723

lmY: 0.481664 +/- 0.045724

Arima: 0.481665 +/- 0.054201

@@

lmD: 0.001364 +/- 0.01878

lmY: 0.001365 +/- 0.018781

Arima: 0.001365 +/- 0.01932

@@

lmD: -0.018679 +/- 0.017374

lmY: -0.018679 +/- 0.017374

Arima: -0.018679 +/- 0.017837

@@

lmD: 0.496018 +/- 0.071855

lmY: 0.496024 +/- 0.071857

Arima: 0.496022 +/- 0.080622

@@

lmD: 0.597354 +/- 0.08202

lmY: 0.597361 +/- 0.082022

Arima: 0.597357 +/- 0.094227

@@

lmD: 1.432631 +/- 0.148944

lmY: 1.432652 +/- 0.148947

Arima: 1.432652 +/- 0.180994

@@

lmD: 0.001383 +/- 0.000137

lmY: 0.001383 +/- 0.000137

Arima: 0.001383 +/- 0.00016

@@

lmD: 0.00044 +/- 6.1e-05

lmY: 0.00044 +/- 6.1e-05

Arima: 0.00044 +/- 7e-05

@@

lmD: 0.000363 +/- 6.4e-05

lmY: 0.000363 +/- 6.4e-05

Arima: 0.000363 +/- 7.2e-05

@@

lmD: 4e-05 +/- 3.3e-05

lmY: 4e-05 +/- 3.3e-05

Arima: 4e-05 +/- 3.8e-05

@@

lmD: 5e-06 +/- 2.9e-05

lmY: 5e-06 +/- 2.9e-05

Arima: 5e-06 +/- 3.4e-05

@@

lmD: 0.000968 +/- 0.000108

lmY: 0.000968 +/- 0.000108

Arima: 0.000968 +/- 0.000125

@@

lmD: 0.001126 +/- 0.000119

lmY: 0.001126 +/- 0.000119

Arima: 0.001126 +/- 0.000138

@@

lmD: 0.036713 +/- 0.003659

lmY: 0.036714 +/- 0.003659

Arima: 0.036714 +/- 0.00425

@@

lmD: 0.203753 +/- 0.246152

lmY: 0.20379 +/- 0.246156

Arima: 0.191314 +/- 0.355242

@@

lmD: 0.066924 +/- 0.186933

lmY: 0.066947 +/- 0.186936

Arima: 0.031787 +/- 0.332858

@@

lmD: 0.108038 +/- 0.185587

lmY: 0.10806 +/- 0.18559

Arima: 0.07227 +/- 0.320898

@@

lmD: -0.047504 +/- 0.172428

lmY: -0.047493 +/- 0.17243

Arima: -0.093727 +/- 0.32618

@@

lmD: -0.06805 +/- 0.171992

lmY: -0.068039 +/- 0.171995

Arima: -0.113836 +/- 0.324815

@@

lmD: 0.1818 +/- 0.225799

lmY: 0.181836 +/- 0.225802

Arima: 0.164846 +/- 0.343081

@@

lmD: 0.192758 +/- 0.234509

lmY: 0.192794 +/- 0.234513

Arima: 0.178049 +/- 0.348128

@@

lmD: 0.372906 +/- 0.252445

lmY: 0.372932 +/- 0.252449

Arima: 0.373033 +/- 0.257109

@@

lmD: 0.000567 +/- 0.000291

lmY: 0.000567 +/- 0.000291

Arima: 0.000567 +/- 0.000322

@@

lmD: 0.000397 +/- 0.000226

lmY: 0.000397 +/- 0.000226

Arima: 0.000393 +/- 0.000269

@@

lmD: 0.000416 +/- 0.000234

lmY: 0.000416 +/- 0.000234

Arima: 0.000413 +/- 0.000274

@@

lmD: 0.000209 +/- 0.000208

lmY: 0.000209 +/- 0.000208

Arima: 0.000203 +/- 0.000261

@@

lmD: 0.000194 +/- 0.000208

lmY: 0.000194 +/- 0.000208

Arima: 0.000187 +/- 0.000261

@@

lmD: 0.000565 +/- 0.000272

lmY: 0.000565 +/- 0.000272

Arima: 0.000565 +/- 0.000304

@@

lmD: 0.000571 +/- 0.00028

lmY: 0.000571 +/- 0.00028

Arima: 0.000571 +/- 0.000312

@@

lmD: 0.008989 +/- 0.005522

lmY: 0.008989 +/- 0.005522

Arima: 0.009015 +/- 0.00575

@@

Arima: 0.215796 +/- 0.040986

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 1 row containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 339.1753 +/- 35.87673

@@

lmY: 123.4768 +/- 11.47021

@@

lmY: 0.228163 +/- 0.054288

@@

lmY: 0.174806 +/- 0.039192

@@

\begin{verbatim}
2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
\end{verbatim}
